An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/eval.tex
ruzica
config: impl
config: first part in eval

\section{Implementation}

\ennan{We need to describe how do we implement each module. We may need to
have three paragraphs: one is for translator, one is for learner 
and one is for checker.}

\section{Evaluations}

We mainly conduct three parts of experiments to evaluate our \app
prototype. We want to answer several questions:

@@

\subsection{\app's effectiveness}

In order to evaluate the effectiveness of \app, we extract
20 misconfiguration files from a MySQL dataset~\cite{xu15hey},
and perform \app on them. \ennan{Here, we first need a table to 
list each configuration error with error type, description,
and whether \app correctly reports the issues.}

Next, we inject some errors to correct configuration files,
and run \app to check whether our framework can correctly detect
these injected errors. \ennan{We also need a table here, 
and list each injected problem.}

Finally, we check suspicious values.

>>>>

\section{Evaluations}
\label{sec-eval}

We conduct three parts of experiments to evaluate our \app
prototype. We want to answer several questions:

@@

\subsection{\app's Effectiveness}

We now apply \app to check against real-world misconfiguration problems.
We use a real misconfiguration dataset~\cite{xu15hey}
that are collected from several online forums, \eg, 
Stack Overflow and MySQL forum.
Each configuration file in this dataset was posted by 
programmers or system administrators, 
when they confront the misconfiguration issues in practice.
This dataset contains 261 incorrect MySQL configuration files.

We apply \app to learn and check the configuration files in this
dataset. Then, we observe how many errors \app can detect,
and manually check whether these detected errors are indeed
configuration errors.
For all the 261 configuration files, we found \app is
able to report all the errors correctly.
For 217 of the 261 configuration files, we found \app's 
error detection results are correct and accurate,
\ie, correctly report the real misconfiguration problem.
However, for 44 of them, \app outputs relatively high false positives,
\eg, higher than 50 false positives,
which is not very helpful to users in practice.
The reason is our training set contains too many incorrect configuration
files, which produce a lot of noises to our learning process,
thus resulting in so many false positives.

In order to clearly evaluate the effectiveness of \app,
we extract 20 incorrect configuration files from the dataset.
As a case study, we present the problem descriptions of these files, 
the types of their errors, and the outputs produced by \app.
Table~\ref{table-casestudy} details this information.

As shown in Table~\ref{table-casestudy},
we found \app is capable of detecting many configuration errors previous
efforts, \eg, EnCore~\cite{zhang14encore}, cannot deal with.
To the best of our knowledge, no existing effort
is able to detect fine-grained value correlation errors in the 
MySQL configuration files.
For example, the third case in Table~\ref{table-casestudy}
presents \app detects the fine-grained correlation,
{\tt key\_buffer\_size} should be larger than 
{\tt sort\_buffer\_size} * {\tt max\_connections}.
